\begin{center}
	{\fontsize{14}{16}\selectfont\textbf{Acknowledgement}}
\end{center}

This thesis would not have been possible without the help, support, and guidance of many people. 

First and foremost, I would like to express my gratitude to Mr. Do Tuan Anh, my supervisor, for his unconditionally enthusiastic teaching and guidance. Although I have worked with him for almost three years, I have never ceased to be amazed at his vision as well as his perseverance in all fields he is involved in, which inspires me so much in my studies and life. Thanks to him, I have a chance to directly work in two different fields in my major, gaining more experience that not all students have the opportunity to partake in. Thank you for always helping and trusting me during my short student life.

Second, I would like to thank Associate Professor Huynh Thi Thanh Binh for allowing me to participate in the Modelling, Simulation Optimization Laboratory (MSO Lab). Her tolerance and training in all facets of being a competent research scientist are deeply appreciated. By the way, I also want to thank the MSO Lab team, especially Mr. Ta Bao Thang and one of my fellow, Le Van Cuong, for always helping me during the time I worked at the lab. Thanks to everyone, the seemingly dry research work became extremely interesting and attractive. 

Next, I would like to thank my classmates in class LTU16A, Course 62, at Hanoi University of Science and Technology. In particular, I would like to thank the monitor Nguyen Nam Anh, who accompanied me through the hard study process, as well as helped me a lot in my studies. I wish you all good health, and soon achieve your goals after graduation.

Finally, I would like to express my deep gratitude to my family and three close friends, Dang Diem Quynh, Dong Quang Linh, and Nguyen Truong Giang. Thanks to the trust and support of family and friends, I was greatly motivated to complete my studies at the school. My youth would not be perfect without you all.
